Testing cosmic isotropy and homogeneity with \textsl{Gaia} quasars

### 2022-08-12 paper/main.tex
Updates from Overleaf

\begin{figure}[t!]
  \begin{mdframed}
  \color{captiongray}
  \begin{center}
    \includegraphics[width=\widefigurewidth]{notebooks/radec.png}
  \end{center}
    \caption{The full quasar sample plotted on the sky in Equatorial coordinates.
    The NGC subsample (and its associated random catalog) is colored blue and the SGC subsample is colored orange.\label{fig:radec}.}
  \end{mdframed}
\end{figure}

\begin{figure}[t!]
  \begin{mdframed}
  \color{captiongray}
  \begin{center}
    \includegraphics[width=\widefigurewidth]{notebooks/lb_better.png}\\
    \includegraphics[width=\widefigurewidth]{notebooks/lb_random_better.png}
  \end{center}
    \caption{The full quasar sample (top) and a sampling of the much larger random catalog (bottom), plotted on the sky in Galactic coordinates.
    This projection is designed to be equal-area, such that a set of quasars uniformly distributed on the sky would make a set of points uniformly distributed on this 2-d plot.
    The NGC subsample (and its associated random catalog) is colored blue and the SGC subsample is colored orange.\label{fig:lb}.}
  \end{mdframed}
\end{figure}

@@

\begin{figure}[t!]
  \begin{mdframed}
  \color{captiongray}
  \begin{center}
    \includegraphics[width=\figurewidth]{notebooks/cumulativeDD.png}
  \end{center}
    \caption{The cumulative total number of quasar--quasar pairs as a function of separation for the NGC and SGC subsamples.
    This figure demonstrates that the fractal dimension is extremely close to 3. The small offset between the NGC and SGC comes from the differing sizes of the two regions.\label{fig:cumulative}.}
  \end{mdframed}
\end{figure}

>>>>

\begin{figure}[t!]
  \begin{mdframed}
  \color{captiongray}
  \begin{center}
    \includegraphics[width=\figurewidth]{notebooks/radec.png}
  \end{center}
    \caption{The full quasar sample plotted on the sky in Equatorial coordinates.
    The NGC subsample (and its associated random catalog) is colored blue and the SGC subsample is colored orange.\label{fig:radec}.}
  \end{mdframed}
\end{figure}

\begin{figure}[t!]
  \begin{mdframed}
  \color{captiongray}
  \begin{center}
    \includegraphics[width=\figurewidth]{notebooks/lb_better.png}\\
    \includegraphics[width=\figurewidth]{notebooks/lb_random_better.png}
  \end{center}
    \caption{The full quasar sample (top) and a sampling of the much larger random catalog (bottom), plotted on the sky in Galactic coordinates.
    This projection is designed to be equal-area, such that a set of quasars uniformly distributed on the sky would make a set of points uniformly distributed on this 2-d plot.
    The NGC subsample (and its associated random catalog) is colored blue and the SGC subsample is colored orange.\label{fig:lb}.}
  \end{mdframed}
\end{figure}

@@

\begin{figure}[t!]
  \begin{mdframed}
  \color{captiongray}
  \begin{center}
    \includegraphics[width=\figurewidth]{notebooks/cumulativeDD.png}
    \includegraphics[width=\figurewidth]{notebooks/cumulativeDD_DR.png}
  \end{center}
    \caption{\textsl{Top:} The cumulative total number of quasar--quasar pairs as a function of separation for the NGC and SGC subsamples. Jackknife uncertainty estimates are shown but are smaller than the points for all points.
    \textsl{Bottom:} The same, but divided by the expectation in a homogeneous universe.
    In this case the expectation is estimated with $DR + RD - RR$ (see text for explanation).
    This figure demonstrates that the fractal dimension is extremely close to 3.\label{fig:cumulative}.}
  \end{mdframed}
\end{figure}
